Did COVID-19 Induce A Strenuous Effect on the 311 Non-Emergency Services System?

### 2022-07-04 README.Rmd
update

```{r zip_dtc, fig.height = 3,fig.width=8}
#scatter plot
zip %>% 
  ggplot(aes(y = daytoclose_diff, x = rate, size = daytoclose_2019, col = ZIP))+
  geom_point()+
  geom_smooth(method=lm)+
  facet_wrap(~CATEGORY, scale = "free_y")+
  theme_bw()+
  theme(legend.position = "none")
```

@@

>>>>

```{r zip_dtc, fig.height = 3,fig.width=8}
#scatter plot
zip %>% 
  ggplot(aes(y = daytoclose_diff, x = rate, size = daytoclose_2019, col = ZIP))+
  geom_point()+
  geom_smooth(method=lm)+
  facet_wrap(~CATEGORY, scale = "free_y")+
  labs(y = "Change in Response Time",x = "COVID-19 infection rate")+
  theme_bw()+
  theme(legend.position = "none")
```

@@

```{r}

zip_covid %>% left_join(zip_covid_311) %>%
  ggplot(aes(x = rate, y = n_allcovid))+ 
  geom_point()+
  geom_smooth(method=lm)+
  labs(x= "COVID-19 infection rate", y="Volume of covid-related requests")+
  theme_bw()
